Learning to Synthesize Rules for Rule-based Intrusion Detectors

### 2020-03-06 paper/paper.tex
pass section 7

\noindent
\textbf{Alternative methods for rule synthesis.} We discuss in the
following techniques similar in goal to ours. Unfortunately, we could
not access the tools implementing the techniques for side
comparison. Nevertheless, we found that there are important
differences between our work and related work. Vollmer
\etal{}~\cite{vollmer-etal-cics2011} propose the use of search to
derive rules for Snort, which are very similar to \suri's.  Their
approach focuses on icmp attacks. It models every field of the icmp
packet in the chromosome of candidate solutions (\ie{}, a rule) of a
genetic search. The initial population is a set of candidate solutions
that randomly combine options, modelling the packet fields. They show
that they were able to generate rules without false negatives and only
3 false positives across 33K benign packets. The key differences
between our work and Vollmer~\etal{}'s are 1) the support of different
protocols and 2) the use of ranking to discriminate alternative
plausible rules. As for 1, our approach supports a variety of
protocols and options that refer to message payloads which
significantly increase the search space. Note that icmp rules only
refer to message fields (see Section~\ref{sec:rules-and-packets}). As
for 2, our solution additionally ranks plausible options, which
contain \emph{no} false positives or negatives with respect to the
benign and mallicious traffic considered. Muthuregunathan
\etal{}~\cite{muthuregunathan-etal2009} propose a clustering method to
create rules. They characterize candidate solutions as a set of field
values and use a clustering algorithm---hybrid k-means partitioned
around menoids---to isolate mallicious from benign
traffic. Subsequently, they optimize the formed clusters using genetic
algorithms and hill-climbing search. Ou approach differs from theirs
in the method used, results, and support for content
options. Kao~\etal~\cite{Kao2015AutomaticNR} proposed ARGS, a system
to synthesize http rules that take mallicious traffic as input. ARGS
looks for a common pattern across the different inputs to define
rules. It does not take existing rules as input or benign
traffic. Consequently, false positive can be produced and need to be
handled manually by users. Our approach, in contrast, does not
generate false positives w.r.t. the input traffic.

>>>>

\noindent
\textbf{Alternative methods for rule synthesis.} We discuss in the
following techniques similar in goal to ours. Unfortunately, we could
not access the tools implementing the techniques for side
comparison. Nevertheless, we found that there are important
differences between our work and related work. Vollmer
\etal{}~\cite{vollmer-etal-cics2011} propose the use of search to
derive rules for Snort, which are very similar to \suri's.  Their
approach focuses on icmp attacks. It models every field of the icmp
packet in the chromosome of candidate solutions (\ie{}, a rule) of a
genetic search. The initial population is a set of candidate solutions
that randomly combine options, modelling the packet fields. They show
that they were able to generate rules without false negatives and only
3 false positives across 33K benign packets. The key differences
between our work and Vollmer~\etal{}'s are 1) the support of different
protocols and 2) the use of ranking to discriminate alternative
plausible rules. As for 1, our approach supports a variety of
protocols and options that refer to message payloads which
significantly increase the search space. Note that icmp rules only
refer to message fields (see Section~\ref{sec:rules-and-packets})
\Luc{eh possivel incluir contents em regras icmp tb. o q a secao 2.3 
diz q \textbf{geralmente} as regras nao-http possuem apenas field options}. 
As for 2, our solution additionally ranks plausible options, which
contain \emph{no} false positives or negatives with respect to the
benign and mallicious traffic considered. Muthuregunathan
\etal{}~\cite{muthuregunathan-etal2009} propose a clustering method to
create rules. They characterize candidate solutions as a set of field
values and use a clustering algorithm---hybrid k-means partitioned
around menoids---to isolate mallicious from benign
traffic. Subsequently, they optimize the formed clusters using genetic
algorithms and hill-climbing search. Ou approach differs from theirs
in the method used, results, and support for content
options. Kao~\etal~\cite{Kao2015AutomaticNR} proposed ARGS, a system
to synthesize http rules that take mallicious traffic as input. ARGS
looks for a common pattern across the different inputs to define
rules. It does not take existing rules as input or benign
traffic. Consequently, false positive can be produced and need to be
handled manually by users. Our approach, in contrast, does not
generate false positives w.r.t. the input traffic.
